\textbf{Influence of galaxy rotation and outflows \\ in the Lyman Alpha spectral line}

### 2016-02-25 abstract/abstract.tex
nuevo abstract

Young galaxies in the Universe have a strong Ly-$\alpha$ emission caused by the ionized Hydrogen atoms in their interstellar medium. When the spectrum of a galaxy has an intense peak around the Ly-$\alpha$ natural frequency ($2.46\times 10^{15}$ Hz) it is called a Lyman Alpha Emitter (LAE). Typical LAEs are very distant ($z \gtrsim 2$). This makes that all the data astronomers can obtain from them is their spectra, and from there all the physical information of the galaxy must be derived. Trying to solve this task requires the creation of a simplified and solid model. In this monograph I propose to consider LAEs as a spherical distribution of Hydrogen atoms that undergoes a solid body rotation and a radial expansion, as seen in Fig. \ref{model}.

\begin{figure}[h]
	%uncomment next line to include a graphic file
	\centerline{\includegraphics[width=4cm]{model.png}}
	\caption{Model of a Expanding and Rotating LAE.}
	\label{model}
\end{figure}

I simulate the effect of rotational velocity, outflow velocity and optical depth of the LAE in the outgoing spectra. The main conclusion is that this new model reproduces LAEs observed features in a clear way and with consistent physical parameters. However, proper observational fits are left for future work. This monograph accomplishes the objective of extracting as much information as possible from a LAE's Ly-$\alpha$ line.

%... a few optional references, such as \cite{Verhamme06}\\

>>>>

Radiative transfer MonteCarlo simulations are nowadays a required tool
to interprete the Lyman-$\alpha$ line morphology. In this work we
explore a new model that computes the join effect of outflows and
bulk rotation. The main conclusion is that rotation and a modest
outflow velocity is enough to reproduce the primary characteristics of
observed LAEs. 
We will show results of adjusting observational data for some selected
objects to models with and without bulk rotation. We finalize by
discussing the possible implications for these results in terms of the
energetics required for supernova feedback and outflows in high
redshift galaxies.
